---
title: "p8105_mtp_zz3168"
author: "Zixuan Zhang"
date: "2023-10-20"
output: github_document
---

```{r}
library(readr)
library(readxl)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(tidyr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 10, 
  fig.height = 9,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1 
##Data import, cleaning, and quality control
We import, organize, and merge data sets, and then delete erroneous data from the merged table through identification. Then we use statistics and visualization to analyze and identify trends in the data set.

The original data includes New York City's COA data from 2018 to 2022 and `zip_data` data that accurately reflects New York City's counties, boroughs, and communities. These include `borough` variables, `net_change` variable, `zip_code`, `month` and other important data.

We first synthesize the COA data from 2018 to 2022 in `coa_data`, then convert the time into `month`, `year`, `date`, and use `total_perm_in - total_perm_out` to get the data of `net_change`. By combining the data of `zip_data` and `coa_data`, we found that some erroneous overlaps appeared in the total data table, and obtained a new data table through exclusion.


```{r}
coa_data_1 = read_xlsx("data/USPS CHANGE OF ADDRESS NYC.xlsx", sheet = c("2018")) 
  coa_data_2 = read_xlsx("data/USPS CHANGE OF ADDRESS NYC.xlsx", sheet = c("2019")) 
coa_data_3 = read_xlsx("data/USPS CHANGE OF ADDRESS NYC.xlsx", sheet = c("2020")) 
coa_data_4 = read_xlsx("data/USPS CHANGE OF ADDRESS NYC.xlsx", sheet = c("2021")) 
coa_data_5 = read_xlsx("data/USPS CHANGE OF ADDRESS NYC.xlsx", sheet = c("2022"))

coa_data = 
  bind_rows(coa_data_1,coa_data_2,coa_data_3,coa_data_4,coa_data_5) |> 
  janitor::clean_names() |> 
  mutate(time = month) |> 
  separate(month, into = c("year", "month", "date") ) |> 
  mutate(net_change = total_perm_in - total_perm_out) |> 
  rename(zip_code = zipcode) 
 



zip_data = read_csv("data/Zip Codes.csv") |> 
  janitor::clean_names() |> 
  mutate(borough = ifelse(county_name == "New York", "Manhattan", county_name)) 


  
combine_data = 
  inner_join(zip_data, coa_data,by="zip_code") |> 
  filter(!(borough == "Manhattan" & zip_code == 10463) &
          !(borough == "Manhattan" & zip_code == 11201 &
          !(borough == "New York" & zip_code == 11239) &
            !(borough == "New York" & zip_code == 11693)
  ))
  
  

```

##describe Tidy Dataset

```{r}
unique_zips =
  combine_data |> 
  select(zip_code) |> 
  distinct() |> 
  knitr::kable()

unique_neighborhoods =
  combine_data |> 
  drop_na() |> 
  select(neighborhood) |> 
  distinct() |> 
  knitr::kable()
  

```

##Compare city
#manhateen
```{r}
combine_data |> 
  filter(borough == "Manhattan") |> 
  count(city) |> 
  arrange(desc(n)) |> 
  mutate(rank = row_number()) |> 
  filter(rank < 7) |> 
  knitr::kable()
  
```

#queen
```{r}
combine_data |> 
  filter(borough == "Queens") |> 
  count(city) |> 
  arrange(desc(n)) |> 
  mutate(rank = row_number()) |> 
  filter(rank < 7) |> 
  knitr::kable()
```


## Problem 2
#EDA
```{r}
combine_data |> 
  group_by(borough, year) |> 
  summarize(average_df = mean(net_change, na.rm = TRUE)) |> 
  mutate(year = as.integer(year)) |> 
  knitr::kable()


```

##lowest values and highest 
```{r}
combine_data |> 
  arrange(net_change) |> 
  select(zip_code, neighborhood, year, month, net_change) |> 
  head(n = 5) |> 
  knitr::kable()


combine_data |> 
  filter(year < 2020) |> 
  arrange(desc(net_change)) |> 
  select(zip_code, neighborhood, year, month, net_change) |> 
  head(n = 5) |> 
  knitr::kable()

  

```


## Visualization:
```{r}
combine_plot = 
  combine_data |> 
  mutate(month = as.integer(month),
         year = as.integer(year))


combine_plot |> 
  group_by(year, time, neighborhood, borough) |> 
  summarize(average_change = mean(net_change, na.rm = TRUE)) |> 
  ggplot(aes(x = time, 
             y = average_change, 
             color = neighborhood)
       ) +
  geom_point()+
  geom_line() + 
  facet_wrap(~borough) +
  labs(title = "Monthly Net Change across Neighborhoods", 
       x = "Time", 
       y = "Average Net Change")



# Export the plot
ggsave("results/city change.pdf")

```

